---
title: 'RMarkdown:  In Class Assignment'
author: Samuel Nunez
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```

Reminders:

-   You do not need to memorize Markdown syntax.
-   You are expected to look things up using:
    -   RStudio’s Markdown Help
    -   Online documentation or examples
-   Click Knit as you go to check that your document still renders correctly.
-   Commit at the end, but consider committing as you go as well.

# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

-   Make a *subsection* called Wise Words.
-   Put your favorite quote in a block quote.
-   Add a working, clickable link to a website that provides more information about that quote.
-   Make another *subsection* called "I recommend", and add some information about your favorite author or musician:
    -   A *subsubheading* with the name of the artist or author;\
    -   An example of their writing or lyrics (formatted in a *block of text*);\
    -   A *list* of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.

# Your work here

## Wise Words

> "Life moves pretty fast. If you don't stop and look around once in a while, you can miss it." - Ferris Bueller.

[Read more in this blog](https://drrichardchambers.com/life-moves-pretty-fast-if-you-dont-stop-and-look-around-once-in-a-while-you-could-miss-it-ferris-bueller/)

## I recommend

### Junkyard Cat

**Talk About It Later** - Junkyard Cat
``` 
And you talk, and talk, and talk
And laugh and kick your feet
But I know, I know, just what you need
Just let it be you and me
And not one thing more
Cause I'm trying to listen
But my mind's been decomissioned
What you say?
How'd You say it?
...

```

Songs Performed:

-   **Talk About It Later**
-   **Where to Start**
-   **Henry**
-   **More than Just Friends**

# Part 2: Code Chunks

```{r echo = TRUE}
2 + 2
```

Complete the following steps:

-   Knit the document and observe what appears in the output.
-   Change the chunk option echo=TRUE to echo=FALSE.
-   Knit the document again.
-   Finally, write 2–3 sentences answering the following questions:
    -   What changed between the two outputs?
    -   Did the calculation still run when the code was hidden?
    -   Why might someone want to hide code in a report?
    -   Why might someone want to show code in a report?

>Setting the option echo to TRUE shows the code when you knit the file, and doesn't when it is set to FALSE. The calculation still runs and displays regardless of the echo status (TRUE|FALSE). I think someone would choose to hide it to make the document a little more polished and hide the complex information that a reader doesn't need to know. They could also choose to show the code as a way to show what formula/equation is being used in the calculation.

# Part 3: A small R-in-markdown preview

-   Create a subsection within this section called About this document.
-   Write 2–3 sentences describing what this document is and what it produces.
-   Include one value generated by inline R code.

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

# About this document

>In this document, I practiced using R Markdown by using heading, subtitles, subsubheadings, block quotes, hyperlinks,and text/code blocks. We used these to create a recommendation for an artist, included lyrics, and also listed songs that the band has performed. I also practiced using r chunks to output a report, for example 2 + 2 will result in `r 2+2`, which is generated using an inline code.
Today's date: `r Sys.Date()`

# Submitting Instructions

When you are finished:

-   Knit the document so that it produces an html file.
-   Stage, commit, and push:
    -   The updated `.rmd` file
    -   The generated `.html` file
-   Submit the GitHub link to the assignment on Canvas.
